---
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#",
  fig.width = 10, fig.height = 5,
  fig.align = "center",
  fig.path  = "man/Figure/",
  dev = 'svg'
)
```

# Data of Kong2023JGRA China HI-STHW  

<!-- [![R-CMD-check](https://github.com/eco-hydro/phenofit/workflows/R-CMD-check/badge.svg)](https://github.com/eco-hydro/phenofit/actions)
[![codecov](https://codecov.io/gh/eco-hydro/phenofit/branch/master/graph/badge.svg)](https://app.codecov.io/gh/eco-hydro/phenofit) -->
[![License](http://img.shields.io/badge/license-GPL%20%28%3E=%202%29-brightgreen.svg?style=flat)](http://www.gnu.org/licenses/gpl-2.0.html)
[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.10360695.svg)](https://doi.org/10.5281/zenodo.10360695)

<!-- [![CRAN](http://www.r-pkg.org/badges/version/phenofit)](https://cran.r-project.org/package=phenofit)
[![total](https://cranlogs.r-pkg.org/badges/grand-total/phenofit)](https://cran.r-project.org/package=phenofit)
[![monthly](https://cranlogs.r-pkg.org/badges/phenofit)](https://cran.r-project.org/package=phenofit)
[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.5150204.svg)](https://doi.org/10.5281/zenodo.5150204) -->


# Data lists

```{r, include=FALSE, message=FALSE}
library(Ipaper)
```


## Figure 2

```{r}
load("./dat_Figure2_annual_variation_STHW.rda")
print2(data_obs, data_sim, ts)
```
- data_obs: observations (OBS)

- data_sim: GCM simulations (SIM)

- `ts`: trend of OBS and SIM

**Vairables**

- `type_adj`: (1) adj: QDM bias-corrected; (2) nonadj: without QDM
- `prob`    : the threshold of HW definition, use 0.95 by default
- `value`   : values of HI-STHW characteristics

## Figure 3

```{r}
load("./dat_Figure3_spatial_trend_STHW.rda")
str(df)
```
**Variables: **

- `type`: (1) OBS: observations; (2) ALL: CMIP6 ALL simulations

- `mask`: (1) `TRUE`: trend is significant; (2) `FALSE`: trend is nonsignificant

## Figure 4

```{r}
load("dat_Figure4_multiple_scenarios.rda")
print2(di_sim, ts)
```

- `ts`: trends of different scenarios

## Figure 5

```{r}
load("dat_Figure5_fingerprint_V3.rda")

print2(d_x, t_x, t_obs, d_noise_a, d_noise_b)
```
- `t_obs`: trends of the observed
- `t_x`: trends of the CMIP6 simulated
- `d_x`: the value of different signal
- `d_noise_a`,`d_noise_b`: noise1 and noise2

## Figure 6

> Figures 6 and 7 share the same data.

```{r}
load("dat_Figure6_HW_char_against_WarmingLevel.rda")
head(df_all)
```

- `value_sm`: smoothed by a 21-year moving window
- `HI_wl`: warming level

## Figure 8

```{r}
df = fread("dat_Figure8_HW_char_in_Spatial.csv")
head(df)
```


# Acknowledgements

Keep in mind that this repository is released under a GPL2 license, which permits commercial use but requires that the source code (of derivatives) is always open even if hosted as a web service.
